Singapore's Public Housing Affordability

### 2023-11-23 datastory.qmd
Project Update

<div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
  <iframe height="800" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
</div>

>>>>

<div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
  <iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
</div>
